### 2021-08-01 paper/paper.tex
first draft of introduction

@@

\trixi\footnote{https://github.com/trixi-framework/Trixi.jl} provides adaptive
high-order numerical simulations of hyperbolic partial differential equations (PDEs)
in Julia \cite{bezanson2017julia}.

\todo{TODO %TODO Introduction
\begin{itemize}
  \item Why we created \trixi
  \item Overview of the paper \etc
\end{itemize}}

\section{Design of \trixi and overview of its features}

@@

\section{Assessment of Julia for simulation-focused scientific computing}

@@

\section{Summary and conclusions}

>>>>

% Allow breaking URLs at hyphens
\PassOptionsToPackage{hyphens}{url}

@@

We are broadly interested in simulation-focused scientific computing, in particular
in hyperbolic partial differential equations (PDEs), computational fluid dynamics (CFD),
and related problems. The focus of our research ranges from specific applications
in CFD over general multi-physics coupling strategies to the required high-order
numerical methods themselves. In addition, we are academics and involved in teaching
students in these areas of science. Thus, we would like to have a code that is
\begin{enumerate}
  \item extendable to be useful for research and development
  \item easy to apply/understand to be useful for students/collaborators
  \item fast enough to be useful not only for small toy problems
\end{enumerate}
Additionally, we are greedy\footnote{See \url{https://julialang.org/blog/2012/02/why-we-created-julia/}} and want to have all these features in a single code.
Roughly one year of collaborative work has resulted in the current version of
\trixi\footnote{https://github.com/trixi-framework/Trixi.jl}, providing adaptive
high-order numerical simulations of hyperbolic partial differential equations (PDEs)
in Julia \cite{bezanson2017julia}. Starting as an experiment, we have been able
to reach more and more of our goals with \trixi.

\todo{TODO: Jesse wants to write about the \trixi community} %TODO: Jesse

In this article, we present an overview of the main features and design decisions
of \trixi in Section~\ref{sec:design-of-trixi}, laying the ground for an extendable
and easy-to-use framework of high-order methods for hyperbolic PDEs. Next, we
compare the serial performance with an established HPC Fortran code in
Section~\ref{sec:performance-comparison}, demonstrating that Julia is not generically
slower than traditional HPC languages (and can even be faster in this particular case).
Thereafter, we present an assessment of Julia for simulation-focused scientific
computing based on our experience with \trixi in Section~\ref{sec:assessment-of-julia}.
Finally, we summary our findings and conclusions in Section~\ref{sec:summary}.

\section{Design of \trixi and overview of its features}
\label{sec:design-of-trixi}

@@

\section{Assessment of Julia for simulation-focused scientific computing}
\label{sec:assessment-of-julia}

@@

\section{Summary and conclusions}
\label{sec:summary}
